Symmetric Peer-to-Peer Applications

### 2022-11-07 final/p2p-22.tex
...

%\author{\fnm{Francisco} \sur{Sant'Anna} \email{francisco@ime.uerj.br}}
%\affil{\orgdiv{Department of Computer Science}, \orgname{Rio de Janeiro State University}, \orgaddress{\country{Brazil}}}

@@

>>>>

\author{\fnm{Francisco} \sur{Sant'Anna} \email{francisco@ime.uerj.br}}
\affil{\orgdiv{Department of Computer Science}, \orgname{Rio de Janeiro State University}, \orgaddress{\country{Brazil}}}

@@

\section*{Declarations}

\subsection*{Ethics Approval}

Not applicable

\subsection*{Conflict of Interest}

The author declares no conflicts of interest.

\subsection*{Data Availability}

Not applicable

\subsection*{Author Contribution}

Francisco Sant'Anna is the single author and wrote the full manuscript.

\subsection*{Funding}

This study was partially funded by FAPERJ (grant E-26/211.329/2019 (251640)).

\subsection*{Consent to publish}

The author hereby expresses consent to publish.
